---
title: "Plotting BNF Interactions"
---

```{r, warning=FALSE, message=FALSE}
library(rvest)
library(magrittr)
library(stringr)
library(stringi)
library(tidyverse)
```

Creating the drugs look-up.
```{r}
#Get a list of links to test
drugs_list <- readLines("https://bnf.nice.org.uk/interaction/") %>%
  str_match_all("<a href=\"(.*?)\"><span>(.*?)</span>") %>%
  unlist() %>%
  data.frame()

#Replace odd characters
drugs_list$. <- str_replace(drugs_list$., "&#233;", replacement = "é")

#Create a dataframe from it.
drugs_list <-  drugs_list %>%
  data.frame(cbind(observation = rep(1:(nrow(drugs_list)/3), each=3))) %>%
  data.frame(cbind(class = c("String", "Link", "Title"))) %>%
  rename(value = '.') %>%
  spread(key=class, value=value)

#Remove non-drug links
drugs_list <- drugs_list %>%
  filter(stri_detect_fixed(drugs_list$Link, "title=") == FALSE)

#Remove defunct columns
drugs_list <- drugs_list %>%
    select(-observation) %>%
    select(-String)

#Remove some leftover tags
drugs_list$Title <- str_replace(drugs_list$Title, "<sub>", replacement = "")
drugs_list$Title <- str_replace(drugs_list$Title, "</sub>", replacement = "")

#Add a string column
drugs_list <- cbind(drugs_list, 
                    string = str_replace(drugs_list$Link, ".html", replacement = ""))

#Add CSS tag and URL columns
drugs_list <- cbind(drugs_list, 
                    url = str_c("https://bnf.nice.org.uk/interaction/", 
                                drugs_list$string, ".html"))
drugs_list <- cbind(drugs_list, css_string = str_c("#", drugs_list$string, " .interactant span"))

#Convert to character classes
drugs_list[] <- lapply(drugs_list, as.character)

#Set a timestamp for the data collection
drugs_listDatestamp <- Sys.Date()
```

Export Drugs_List
```{r, eval=FALSE}
drugs_listName <- str_c("archive/", drugs_listDatestamp) %>%
str_replace_all(" ", "") %>%
str_c("drugs_list.csv")

write.csv(drugs_list, drugs_listName)
```

```{r, echo=FALSE}
head(drugs_list, 5)
```

Scrape Data.
```{r}
#Data
data <- sapply(drugs_list$url, function(x)
               read_html(x) %>%
               list())

#Set a timestamp for the data collection
Timestamp <- Sys.time()
Datestamp <- Sys.Date()
```

Constructing the interactions database.
//Create blank spaces for not listed ()
```{r}
##Title
dataframe <- data.frame(Title = drugs_list$Title)

##Interactions
alli <- lapply(data,
                function(url){
                    url %>% 
                    html_nodes(css = ".interactant span") %>%
                    html_text()
                })

##All Severity
##severityi <- lapply(data,
##                function(url){
##                    url %>% 
##                    html_nodes(css = "div.span9.interaction-messages > div") %>%
##                    html_attr("class") %>%
##                    str_replace_all("interaction-message  ", "")
##                })

#Set ordinal factor for severity
severity <- c("NotSet", "Unknown", "Mild", "Moderate", "Severe")
severity <- factor(severity, levels=c("NotSet", "Unknown", "Mild", "Moderate", "Severe"), ordered=TRUE)

#All Severity
severityi2 <- lapply(1:length(data), function(x) {
sections <- html_nodes(data[[x]], "div.span9.interaction-messages")
lapply(1:length(sections), function(x1, x){
#Returns Max value in multiples.
if (length(sections[[x1]]) > 1) {
  sections[[x1]] %>% 
    html_children() %>% 
    html_attr("class") %>% 
    str_replace_all("interaction-message  ", "") %>% 
    max()
  } else {
  sections[[x1]] %>% 
     html_children() %>% 
     html_attr("class") %>%
     str_replace_all("interaction-message  ", "")
  }
  }
) %>%
unlist()
})

data[[52]] %>%
  html_nodes("div.span9.interaction-messages")

##Evidence
#evidencei <- lapply(data,
#                function(url){
#                    url %>% 
#                    html_nodes(css = "dd~ dd") %>%
#                    html_text()
#                })

#All Evidence
evidencei2 <- lapply(1:length(data), function(x) {
sections <- html_nodes(data[[x]], "div.span9.interaction-messages")

lapply(1:length(sections), function(x1, x){
#Returns Max value in multiples.
if (length(sections[[x1]] %>% 
    html_nodes("dd~ dd")) > 0) {
  sections[[x1]] %>% 
    html_nodes("dd~ dd") %>%
    html_text() %>%
    min()
  } else {
  as.character("NotSet")
  }
  }
) %>%
unlist()
})

##Interactions Info
#infoi <- lapply(data,
#                function(url){
#                    url %>% 
#                    html_nodes(css = ".interaction-message div") %>%
#                    html_text() %>%
#                    str_replace_all("\n", replacement="") %>%
#                    str_trim()
#                })

#Combine multiple divs under one interaction
infoi2 <- lapply(1:length(data), function(x) {
sections <- html_nodes(data[[x]], "div.span9.interaction-messages")

lapply(1:length(sections), function(x1, x){
#Returns Max value in multiples.
if (length(sections[[x1]]) > 1) {
  sections[[x1]] %>% 
    html_nodes(css = ".interaction-message div") %>% 
    html_text() %>% 
    str_replace_all("\n", replacement="") %>% 
    str_trim() %>% 
    paste(sep="", collapse="")
  } else {
  sections[[x1]] %>% 
    html_nodes(css = ".interaction-message div") %>% 
    html_text() %>% 
    str_replace_all("\n", replacement="") %>% 
    str_trim()
  }
  }
) %>%
unlist()
})

#Bind columns
dataframe <- cbind(dataframe, 
                           data_frame(alli), 
                           data_frame(severityi2),
                           data_frame(evidencei2),
                           data_frame(infoi2))
#Rename columns
dataframe <-  dataframe %>%
  rename(Interactions = 'alli',
         Severity = 'severityi2', 
         Evidence = 'evidencei2',
         'Interactions Info' = 'infoi2')

##Totals
dataframe$'Interaction Total' <- lapply(1:nrow(dataframe), function(x){
                    unlist(length(alli[[x]]))
                })
dataframe$'Severity Total' <- lapply(1:nrow(dataframe), function(x){
                    unlist(length(dataframe$Severity[[x]]))
                })
dataframe$'Evidence Total' <- lapply(1:nrow(dataframe), function(x){
                    unlist(length(dataframe$Evidence[[x]]))
                })
dataframe$'Interactions Info Total' <- lapply(1:nrow(dataframe), function(x){
                    unlist(length(dataframe$'Interactions Info'[[x]]))
                })
#rm(alli)
#rm(severityi)
#rm(evidencei)
#rm(infoi)

#rm(dataframe)
```

#Incomplete Data
```{r}
dataframe$'Complete Severity' <- lapply(1:1006, function(x){
                    if (dataframe$`Interaction Total`[[x]] == dataframe$`Severity Total`[[x]])
                    {TRUE} else {FALSE}
})
#Count True/False
unlist(dataframe$'Complete Severity') %>%
  summary()
```

```{r}
dataframe$'Complete Interactions Info' <- lapply(1:1006, function(x){
                    if (dataframe$`Interaction Total`[[x]] == dataframe$`Interactions Info Total`[[x]])
                    {TRUE} else {FALSE}
})
unlist(dataframe$'Complete Interactions Info') %>%
  summary()
```

Evidence.
```{r}
dataframe$`Complete Evidence Info` <- lapply(1:1006, function(x){
                    if (dataframe$`Interaction Total`[[x]] == dataframe$`Evidence Total`[[x]])
                    {TRUE} else {FALSE}
})
unlist(dataframe$`Complete Evidence Info`) %>%
  summary()
```
Used the min value, where 2 evidence levels are indicated. (Opposite of the severity).
The rationale being that you should be more cautious, and more skeptical.

```{r}
dataframe$'Complete Data' <- lapply(1:1006, function(x){
                    if (dataframe$`Interaction Total`[[x]] == dataframe$`Severity Total`[[x]] &
                        dataframe$`Interaction Total`[[x]] == dataframe$`Interactions Info Total`[[x]]  &
                        dataframe$`Interaction Total`[[x]] == dataframe$`Evidence Total`[[x]])
                    {TRUE} else {FALSE}
})
unlist(dataframe$'Complete Data') %>%
  summary()
```

Complete Data
```{r}
dataframe %>%
  filter(dataframe$`Complete Data` == TRUE)
```

Export dataframe
```{r, eval=FALSE}
dataframeName <- str_c("archive/", Datestamp) %>%
str_replace_all(" ", "") %>%
str_c("dataframe.Rda")

save(dataframe, file=dataframeName)
```

Make a JSON Format
```{r}
#Create a new database
master <- dataframe %>%
  select('Title', 'Interactions', 'Severity', 'Evidence', 'Interactions Info') %>%
  rename(name = 'Title',
         imports = 'Interactions')
master$title <- master$name
#Relabel 'name'
master$name <- str_c("BNF.", master$name, ".", master$name) %>%
  str_replace_all(pattern=" ", replacement="")

#Relabel 'imports'
node.parent.child <- function(x) {
  example <- master[x,] %>%
    select('imports') %>%
    unlist() %>%
    as.character() 
  
  example <- str_c(".", example) %>%
    str_dup(times=2)
  
  example <- str_c("BNF", example) %>%
    str_replace_all(pattern=" ", replacement="")
  return(as.vector(example))
}
master$imports <- lapply(1:nrow(master), node.parent.child)
```

```{r}
master %>%
  jsonlite::toJSON() %>%
  write(file="archive/flare.json")

jsonName <- str_c("archive/", str_replace_all(Datestamp, " ", ""), "flare.json")

master %>%
  jsonlite::toJSON() %>%
  write(file = jsonName)
```

///

Shortlist top 100.
```{r}
#reclassify title, remove whitespace
master$title <- as.character(master$title) %>%
  trimws("both")

top100master <- master %>%
  filter(master$title %in% top100$X1)
```

Remove imports/ severity / evidence / interactions info.
Find positions of imports not listed. make vector - remove severity / evidence / interactions info.
```{r}
for (i in 1:nrow(top100master)){
   arentindex <- which(!top100master[i,]$imports[[1]] %in% top100master$name)
  top100master[i,]$imports[[1]] <- top100master[i,]$imports[[1]][-c(arentindex)]
  top100master[i,]$Severity[[1]] <- top100master[i,]$Severity[[1]][-c(arentindex)]
  top100master[i,]$Evidence[[1]] <- top100master[i,]$Evidence[[1]][-c(arentindex)]
  top100master[i,]$`Interactions Info`[[1]] <- top100master[i,]$`Interactions Info`[[1]][-c(arentindex)]
}
```

Now introducing some totals for evidence and severity so I don't have to do it in JS.
```{r}
top100master <- top100master %>%
  mutate(mildtot = str_count(top100master$Severity, "Mild")) %>%
  mutate(modtot = str_count(top100master$Severity, "Moderate")) %>%
  mutate(sevtot = str_count(top100master$Severity, "Severe")) %>%
  mutate(nstot = str_count(top100master$Severity, "NotSet"))

top100master <- top100master %>%
  mutate(studytot = str_count(top100master$Severity, "Study")) %>%
  mutate(anectot = str_count(top100master$Severity, "Anecdotal")) %>%
  mutate(theorettot = str_count(top100master$Severity, "Theoretical")) %>%
  mutate(nsetot = str_count(top100master$Severity, "NotSet"))
```

```{r}
top100master %>%
  jsonlite::toJSON() %>%
  write(file="archive/flare100.json")

jsonName100 <- str_c("archive/", str_replace_all(Datestamp, " ", ""), "flare100.json")

master %>%
  jsonlite::toJSON() %>%
  write(file = jsonName100)
```

